dbRDA analysis

### 2017-04-17 doc/RMD/RDA-analysis.Rmd
fix friggen holdovers from old code
This is why you shouldn't copy and paste, kids.
Your code will work one day, but not the next
because you foolishly changed a variable name.

# This was ganked from https://github.com/gavinsimpson/ggvegan/blob/59d233977a5b2d15d4de150b782fb1794aa1de8b/R/utils.R
# 
# @title Scale Vectors to Data
# @description Scale vector arrows to \code{fill} proportion of the data.
# @param arrows a two-column matrix-like object containing coordinates for the arrows/vectors on x and y axes.
# @param data a two-column matrix-like object containing coordinates of the data on the x and y axes.
# @param at numeric vector of length 2; location of the origin of the arrows.
# @param fill numeric; what proportion of the range of the data to fill
# @return a numeric multiplier that will scale the arrows
# @author Gavin L. Simpson
arrowMul <- function(arrows, data, at = c(0, 0), fill = 0.75) {
    u <- c(range(data[,1], range(data[,2])))
    u <- u - rep(at, each = 2)
    r <- c(range(arrows[, 1], na.rm = TRUE), range(arrows[, 2], na.rm = TRUE))
    rev <- sign(diff(u))[-2]
    if (rev[1] < 0)
        u[1:2] <- u[2:1]
    if (rev[2] < 0)
        u[3:4] <- u[4:3]
    u <- u/r
    u <- u[is.finite(u) & u > 0]
    fill * min(u)
}
plot_dbrda <- function(db){
  dbsum     <- scores(db, display = c("cn", "bp", "sites"), scaling = "sites")
  Centroids <- as.data.frame(dbsum$centroids)
  Centroids <- rownames_to_column(Centroids, var = "cent_type")
  Centroids <- mutate_(Centroids, .dots = list(Length = ~sqrt(CAP1^2 * CAP2^2)))
  # Centroids
  SampleCentroids <- rownames_to_column(data.frame(dbsum$sites), var = "isolate_names")

  mul     <- arrowMul(dbsum$biplot[, 1:2], dbsum$sites) * 10
  Arrows  <- data.frame(dbsum$biplot * mul)
  Arrows  <- rownames_to_column(Arrows, var = "class")
  Arrows  <- mutate_(Arrows, .dots = list(Length = ~sqrt(CAP1^2 * CAP2^2)))
  Arrows  <- arrange(Arrows, Length)
  Arrows  <- top_n(Arrows, 8)
  ggplot(DecendCentro, aes(x = CAP1, y = CAP2))+
   geom_point(data = site_centroids, alpha = 1/2, fill = "dark orange", color = "black", size = 2.5, pch = 21)+
   coord_cartesian() +
   geom_segment(aes(x = 0, xend = CAP1, 
                    y = 0, yend = CAP2),
                arrow = arrow(length = unit(0.3, "cm")), 
                data = Arrows
                ) + 
   geom_label_repel(aes(x = CAP1, y = CAP2, label = class), data = Arrows)
}
```

>>>>

# This was ganked from https://github.com/gavinsimpson/ggvegan/blob/59d233977a5b2d15d4de150b782fb1794aa1de8b/R/utils.R
# 
# @title Scale Vectors to Data
# @description Scale vector arrows to \code{fill} proportion of the data.
# @param arrows a two-column matrix-like object containing coordinates for the arrows/vectors on x and y axes.
# @param data a two-column matrix-like object containing coordinates of the data on the x and y axes.
# @param at numeric vector of length 2; location of the origin of the arrows.
# @param fill numeric; what proportion of the range of the data to fill
# @return a numeric multiplier that will scale the arrows
# @author Gavin L. Simpson
arrowMul <- function(arrows, data, at = c(0, 0), fill = 0.75) {
    u <- c(range(data[,1], range(data[,2])))
    u <- u - rep(at, each = 2)
    r <- c(range(arrows[, 1], na.rm = TRUE), range(arrows[, 2], na.rm = TRUE))
    rev <- sign(diff(u))[-2]
    if (rev[1] < 0)
        u[1:2] <- u[2:1]
    if (rev[2] < 0)
        u[3:4] <- u[4:3]
    u <- u/r
    u <- u[is.finite(u) & u > 0]
    fill * min(u)
}
# Plotting the dbRDA results
# 
# @param db a capscale object
# @return a ggplot2 object from the scores 
plot_dbrda <- function(db){
  dbsum     <- scores(db, display = c("cn", "bp", "sites"), scaling = "sites")
  Centroids <- as.data.frame(dbsum$centroids)
  Centroids <- rownames_to_column(Centroids, var = "cent_type")
  Centroids <- mutate_(Centroids, .dots = list(Length = ~sqrt(CAP1^2 * CAP2^2)))
  # Centroids
  SampleCentroids <- rownames_to_column(data.frame(dbsum$sites), var = "isolate_names")

  mul     <- arrowMul(dbsum$biplot[, 1:2], dbsum$sites)
  Arrows  <- data.frame(dbsum$biplot * mul)
  Arrows  <- rownames_to_column(Arrows, var = "class")
  Arrows  <- mutate_(Arrows, .dots = list(Length = ~sqrt(CAP1^2 * CAP2^2)))
  Arrows  <- arrange(Arrows, Length)
  Arrows  <- top_n(Arrows, 8)
  ggplot(Centroids, aes(x = CAP1, y = CAP2))+
   geom_point(data = SampleCentroids, alpha = 1/2, fill = "dark orange", color = "black", size = 2.5, pch = 21)+
   coord_cartesian() +
   geom_segment(aes(x = 0, xend = CAP1, 
                    y = 0, yend = CAP2),
                arrow = arrow(length = unit(0.3, "cm")), 
                data = Arrows
                ) + 
   geom_label_repel(aes(x = CAP1, y = CAP2, label = class), data = Arrows)
}
```
